### 2020-04-23 paper.tex
RP

\subsection{Reactive Programming with RxJS}

\emph{What is RP?}

@@

\subsection{Debugging Concepts}
\begin{itemize}
	\item Imperative
	\item Declarative
	\item Omniscient
\end{itemize}

\subsection{Specialized Reactive Programming Tooling}

>>>>

Salvaneschi et al. \cite{comprehendingReactiveApplications} define the ``Reactive Application'' \emph{(RA)} as a computer program which processes a continuos, indefinite and ever-changing flow of information. It is contrasted by a traditional application which consumes and processes one piece of input while producing a one-off output result: Think of an image format conversion program which takes an HEIF\footnote{\url{https://nokiatech.github.io/heif/technical.html}} image file for input, processes it and outputs an JPEG file likewise.

\begin{figure}[h]
	\centering
	\emph{TODO}

	\caption{Traditional vs. Reactive Application}
	\label{fig:reactive-application}
\end{figure}

Further Salvaneschi et al. provide a set of examples of what a reactive application might achieve with their three-parted classification schema: A \emph{synthetic application} transforms and processes streams of information. hence multiple image conversions one after another or in parallel could be implemented as a synthetic, reactive application. Beside the modelling of pure data flows, reactive applications are prevalent in the area of user interfaces \emph{(UI)}: They can be identified as \emph{interactive applications} and \emph{graphical animations} here.

Various ways of implementing reactive applications emerged over time. The Observer design pattern \cite{observerDesignPattern}, originated in Object Oriented Programming \emph{(OOP)}, is a basic pattern we can find in many of todays API implementations providing reactivity \cite{ownPaper}. Functional Programming \emph{(FP)} experiments with reactive language extensions like the on animations specialized library Fran (Haskell) \cite{SurveyOnReactiveProgramming} or more recently the reactive runtime and DSL REScala (Scala) \cite{10.1145/2577080.2577083}. The declarative nature of FP lead finally to what we understand as ``Reactive Programming'' today.

\subsection{Reactive Programming}

Reactive programming \emph{(RP)} is a programming paradigm.

\subsection{Debugging Concepts}

\begin{itemize}
	\item Imperative
	\item Declarative
	\item Omniscient
\end{itemize}

\subsection{RxJS}

@@
